Case study validations of automatic bullet matching

### 2018-11-16 index.Rmd
features

\svp{The random forest presented in \citet{aoas} takes as input the following characteristics derived from a pair of aligned sequences:}
\hh{We need to think what to do about the list - we could either just say that the random forest is based on multiple features, such as, ... and list three (and refer to the paper). Or we expand quite a bit and define the features in mathy detail using our notation above.}
\svp{\begin{itemize}
\item Cross-correlation 
\item Number of matching striae 
\item Total depth of joint striations 
\item Number of non-matching striae 
\item Euclidian distance between the sequences 
\item Consecutive Matching Striae 
\item Consecutive Non-matching Striae
\end{itemize}}
\svp{The output of the random forest is a score between 0 and 1 representing the algorithm's assessment of the strength of the match, where 1 indicates that the algorithm believes it to be highly likely that the aligned signatures match, and 0 indicates that the aligned signatures are highly likely to originate from different lands.}

# Assessing Match Strength
Each of the features described in the previous section, as well as the random forest score, describe comparisons on a land-to-land basis. While these comparisons are useful, \hh{the question of interest typically involves }  the entire physical object (e.g. all lands on a single bullet).

>>>>

\svp{The random forest presented in \citet{aoas} takes as input the following characteristics derived from a pair of aligned sequences:}

\hh{We need to think what to do about the list - we could either just say that the random forest is based on multiple features, such as, ... and list three (and refer to the paper). Or we expand quite a bit and define the features in mathy detail using our notation above.}
\hh{How about:}
\hh{The random forest presented in \citet{aoas} is based on a combination of multiple characteristics, such as maximized cross-correlation, number of matching striae, and number of consecutively matching striae among others. }

\svp{\begin{itemize}
\item Cross-correlation 
\item Number of matching striae 
\item Total depth of joint striations 
\item Number of non-matching striae 
\item Euclidian distance between the sequences 
\item Consecutive Matching Striae 
\item Consecutive Non-matching Striae
\end{itemize}}
The output of the random forest is a score between 0 and 1 representing the algorithm's assessment of the strength of the match, where scores close to 1 indicate that the algorithm believes it to be highly likely that the aligned signatures come from the same source, while low scores indicate that the aligned signatures are highly likely to originate from different lands.

# Assessing Match Strength
Each of the features described in the previous section, as well as the random forest score, describe comparisons on a land-to-land basis. While these comparisons are useful, \hh{the question of interest typically involves }  the entire physical object (e.g. all lands on a single bullet), \hh{and a conclusion on same or different source should be reached based on the evidence of all lands of the bullets}.
